Crop diversification in a game against nature in a mediterranean agro-ecosystem

### 2020-01-24 risk-percption.Rmd
trace drought risk plot

```{r}
konya <- matrix(c(32.5, 37.9), nrow = 1)
konya <- matrix(c(33.5138, 36.2765), nrow = 1)
```

@@

sim_past <- left_join(precc, precl) %>%
  mutate(rainfall = (precc + precl) * 2.628e+9,
         year = rep(-10200:-5001, each = 12), # add hardcode dates instead of using ncdf time because of date shift with averaging period
         month = rep(1:12, times = 5200)) %>%
  select(-time, -precl, -precc) %>%
  mutate(water_year = if_else(month %in% 10:12, year + 1L, year)) %>% 
  # filter(!(month %in% c(6:9))) %>%
  group_by(water_year) %>%
  add_tally() %>%
filter(n == 12) %>%
  summarise(precip = sum(rainfall))

plot(sim_past)
```

```{r}
plot(sim_past)
```

```{r}
tibble(droughts = (sim_past[1:5150, 2] < 250)) %>%
  mutate(time = rep(1:206, each = 25))%>%
  group_by(time) %>%
  summarise(test = sum(droughts)/25)
```

```{r}
simulation <- accumulate((sim_past$precip < 300), ~learn(.x, .y), .init = agents) %>% 
  bind_rows(.id = 'time') %>%
  mutate(time = as.numeric(time)) %>%
  filter(time != 1)
```

>>>>

```{r}
konya <- matrix(c(32.5, 37.9), nrow = 1)
#konya <- matrix(c(33.5138, 36.2765), nrow = 1)
```

@@

sim_past <- left_join(precc, precl) %>%
  mutate(rainfall = (precc + precl) * 2.628e+9,
         year = rep(-10200:-5001, each = 12), # add hardcode dates instead of using ncdf time because of date shift with averaging period
         month = rep(1:12, times = 5200)) %>%
  select(-time, -precl, -precc) %>%
  mutate(water_year = if_else(month %in% 10:12, year + 1L, year)) %>% 
   filter(!(month %in% c(6:9))) %>%
  group_by(water_year) %>%
  add_tally() %>%
filter(n == 8) %>%
  summarise(precip = sum(rainfall)) %>%
  mutate(drought = precip < 300)
```

```{r, fig.height =3, fig.width = 9}
sim_past %>%
  filter(between(water_year, -9500, -5500)) %>%
  mutate(time_step = ceiling(water_year / 50),
         year = time_step * 50) %>%
  group_by(year) %>%
  summarise(risk = sum(drought) / 50) %>%
  ggplot(aes(year, risk, fill = risk, color = risk)) +
  geom_hline(yintercept = indiff$risk, color = 'black', linetype = 2, width = 1.2) +
  geom_col()  +
  scale_fill_distiller(palette = 'YlOrRd', direction = 1) +
  scale_color_distiller(palette = 'YlOrRd', direction = 1)+
  theme_minimal() +
  labs(x = 'Years BP', y = 'Drought risk')  + theme(legend.position = "none")
```

```{r}
simulation <- accumulate(sim_past$drought, ~learn(.x, .y), .init = agents) %>% 
  bind_rows(.id = 'time') %>%
  mutate(time = as.numeric(time)) %>%
  filter(time != 1)
```
